Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe

### 2023-09-14 NSM_Skinner_Wise/referee/referee_response.tex

Thank you for this recommendation. We have rewritten some of the abstract to include numerical values.

\begin{tcolorbox}[colback={lightgray}]
    4)      It looks like one of the main points of the manuscript is revealing the impacts of NSM on the physical properties of the first galaxies with Pop II star formation. An NSM is an additional feedback source at the point of the first galaxy formation. I think the impact of NSM is degenerated with other factors of Pop III stars like the number of stars in mini-haloes, star formation efficiency, and initial mass function. For example, if three Pop III stars form in mini-halos (e.g., Sugimura et al. 2020, ApJ, 892, L14; Sugimura et al. 2023), they are likely to give similar feedback. The authors should add a discussion about the uniqueness of NSMs at the point of the first galaxy formation.
\end{tcolorbox}

We would like to clarify something in order to respond to this point. The primary focus of this paper is the r-process enhancement of Pop II stars due to a NSM. We are not explicitly focused on the physical properties of the first galaxies. The interesting thing about this scenario, is that if a NSM occurs early in the star formation history of a galaxy, the r-process material that is produced during the merging event can end up in the next generation of stars, like the stars in Ret II. This is precisely what we were investigating. We would like to be able to say something about how the NSM parameters correlate with different Pop II star formation characteristics, but given our small sample size, and the intrinsic randomness of star formation that makes the simulations so different from one another, we cannot say with certainty how the NSM model parameters might affect different trends we may see initially. This is the last bullet point in our conclusion.

The NSM alone should also not have a large dynamical effect on the galaxy. In these early times, when Pop III stars are also forming, they will be the dominant source of energy in the galaxy. We can make an order of magnitude estimate of this. If we consider just the hydrogen ionizing radiation coming from Pop III stars, for a Pop III stellar mass of $10^3$ \Ms, and using the ionizing rates and energies from \citet{Schaerer03}, we find that the hydrogen ionizing stellar energy is $\sim 10^{54}$ erg. About 1\% of this is converted into thermal and kinetic energy, and if we assume that we get about 1 SN per 100 from a Salpeter IMF, we get $\sim 10^{52}$ erg from SNe. The kilonova produced by GW170817 resulted in about $10^{51}$ erg of ejecta energy \citep{Metzger19}. We can see that the energetic effect from Pop III stars is much larger compared to the effects from the kilonova.

### 2023-09-14 NSM_Skinner_Wise/referee/referee_response.tex

Thank you for this recommendation. We have rewritten some of the abstract to include numerical values.

\begin{tcolorbox}[colback={lightgray}]
    4)      It looks like one of the main points of the manuscript is revealing the impacts of NSM on the physical properties of the first galaxies with Pop II star formation. An NSM is an additional feedback source at the point of the first galaxy formation. I think the impact of NSM is degenerated with other factors of Pop III stars like the number of stars in mini-haloes, star formation efficiency, and initial mass function. For example, if three Pop III stars form in mini-halos (e.g., Sugimura et al. 2020, ApJ, 892, L14; Sugimura et al. 2023), they are likely to give similar feedback. The authors should add a discussion about the uniqueness of NSMs at the point of the first galaxy formation.
\end{tcolorbox}

We would like to clarify something in order to respond to this point. The primary focus of this paper is the r-process enhancement of Pop II stars due to a NSM. We are not explicitly focused on the physical properties of the first galaxies. The interesting thing about this scenario, is that if a NSM occurs early in the star formation history of a galaxy, the r-process material that is produced during the merging event can end up in the next generation of stars, like the stars in Ret II. This is precisely what we were investigating. We would like to be able to say something about how the NSM parameters correlate with different Pop II star formation characteristics, but given our small sample size, and the intrinsic randomness of star formation that makes the simulations so different from one another, we cannot say with certainty how the NSM model parameters might affect different trends we may see initially. This is the last bullet point in our conclusion.

The NSM alone should also not have a large dynamical effect on the galaxy. In these early times, when Pop III stars are also forming, they will be the dominant source of energy in the galaxy. We can make an order of magnitude estimate of this. If we consider just the hydrogen ionizing radiation coming from Pop III stars, for a Pop III stellar mass of $10^3$ \Ms{} that is approximately the mean we found in \citep{Skinner20}, and using the ionizing rates and energies from \citet{Schaerer03}, we find that the hydrogen ionizing stellar energy is $\sim 10^{54}$ erg. About 1\% of this is converted into thermal and kinetic energy, and if we assume that we get about 1 SN per 100 from a Salpeter IMF, we get $\sim 10^{52}$ erg from SNe. The kilonova produced by GW170817 resulted in about $10^{51}$ erg of ejecta energy \citep{Metzger19}. We can see that the energetic effect from Pop III stars is much larger compared to the effects from the kilonova.

@@

\begin{tcolorbox}[colback={lightgray}]
    9)      The authors show the coexistence of Pop II and III stars in the first galaxies. Recent theoretical studies showed similar results (Riaz et al. 2022, ApJL, 937, L6; Yajima et al., arXiv2211.12970). It would be good to discuss the mass fraction and distribution of Pop III stars in the first galaxies with the previous works. 
\end{tcolorbox}

Thank you for this suggestion. You are correct that we see similar results! We have added this short comparison to the discussion section. We are leaving the figures we made to make the comparison in this report, but we are electing to not add more plots to the paper.

\begin{figure}[h]
    \centering
    \subfloat[\centering Energy Variation]{{\includegraphics[width=0.4\textwidth]{plots/eng_pop3_ratio.pdf} }}%
    \qquad
    \subfloat[\centering Delay Time Variation]{{\includegraphics[width=0.4\textwidth]{plots/time_pop3_ratio.pdf} }}%
    \caption{The mass fraction of Pop III stars to total stellar mass versus the total stellar mass colored by redshift.}%
    \label{fig:ratio}%
\end{figure}

\begin{figure}[h]
    \centering
    \subfloat[\centering Energy Variation]{{\includegraphics[width=0.4\textwidth]{plots/eng_stpellar_mass.pdf} }}%
    \qquad
    \subfloat[\centering Delay Time Variation]{{\includegraphics[width=0.4\textwidth]{plots/time_stellar_mass.pdf} }}%
    \caption{The total stellar mass of both Pop III and Pop II stars as a function of redshift. The solid lines are the total stellar masses of Pop III stars, and the dashed lines are total stellar masses of Pop II stars.}%
    \label{fig:ratio}%
\end{figure}

### 2023-09-14 NSM_Skinner_Wise/NSM_mixing.tex
Moving around OG definition.

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_evolution.pdf}
	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original run. The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass. The NSM occurs at 286 Myr.}
	\label{fig:eng_evol}
\end{figure}

@@

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_stellar_dist.pdf}
	\caption[Radial distribution of Pop II stars for each explosion energy variation run.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs D, Fiducial and E, and the original \textbf{(OG)} run. The dashed lines indicate the half-mass radius, which are 331.2 pc, 37.1 pc, 65.3 pc, and 50.6 pc for the original run, run D, run Fiducial, and run E, respectively. The virial radius at this time is 1.6 kpc, 1.73 kpc, 1.72 kpc, and 1.73 kpc for the original run, run D, run Fiducial, and run E, respectively.}
	\label{fig:eng_stellar_dist}
\end{figure}

>>>>

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_evolution.pdf}
	\caption[The halo mass, Pop II stellar mass, gas fraction, and r-process mass as a function of time for the explosion energy variation runs.]{The evolution of the main halo in each explosion energy variation run and the original \textbf{(OG)} run. The top panel shows the halo mass, second from the top shows the Pop II stellar mass, third from the top shows the average gas fraction, and the bottom shows the r-process mass. The NSM occurs at 286 Myr.}
	\label{fig:eng_evol}
\end{figure}

@@

\begin{figure} 
	\includegraphics[width=\columnwidth]{plots/eng_stellar_dist.pdf}
	\caption[Radial distribution of Pop II stars for each explosion energy variation run.]{The fraction of Pop II stars that are within some radius at the $z = 10$ for runs D, Fiducial and E, and the original run. The dashed lines indicate the half-mass radius, which are 331.2 pc, 37.1 pc, 65.3 pc, and 50.6 pc for the original run, run D, run Fiducial, and run E, respectively. The virial radius at this time is 1.6 kpc, 1.73 kpc, 1.72 kpc, and 1.73 kpc for the original run, run D, run Fiducial, and run E, respectively.}
	\label{fig:eng_stellar_dist}
\end{figure}
